### 2023-05-06 Draft.Rmd
Updates to the Rmd file + most updated results for appedix analyses + Add groundhog to preprocessing function + removing redundant code from preprocessing scripts

affiliation:
  - id            : "1"
    institution   : "Sagol school of neuroscience, Tel Aviv University"
  - id            : "2"
    institution   : "University Grenoble Alpes, University Savoie Mont Blanc"
  - id            : "3"
    institution   : "School of Psychological Sciences, Tel Aviv University"
  - id            : "4"
    institution   : "Birkbeck, University of London"
  - id            : "5"
    institution   : "Wellcome Centre for Human Neuroimaging, UCL"

@@

library(groundhog)
groundhog.library(c(
  'ggplot2',
  'stringr',
  'gridExtra',
  'grid',
  'ggh4x',
  'ggtext',
  'ggridges',
  'ggpubr',
  'scales',
  'dplyr',
  'tidyr',
  'patchwork',
  'HDInterval',
  'MCMCpack',
  'nleqslv'), '2023-04-10')
# separate github libraries
groundhog.library(c(
  'github::mufcitay/signcon'), '2023-04-10')

@@

```{r run-analyses, include=FALSE}
# run all analyses. The outputs are later used in the script
source('datasets_analysis\\run_all_analyses.R')

# sourcing the 'fig1sim' script generates the panels populating Figure 1 in the
# manuscript, and analyzes the simulated data with all available non-directional
# tests, and t-tests.
source('figures\\fig1sim.R')
# sourcing the 'fig2_3' script generates figure2,4 and supplementary figure 1,2
# it also analyzes the results of all datasets according to all tests
source('figures\\fig2_3.R')
# sourcing the 'fig4' script generates figure4.
# it also analyzes the results of all datasets according to all tests
source('figures\\fig4.R')
source('appendix\\appendix_A.R')
appendix_A_res <- run_appendixA(conf_FAs, conf_sensitivity)

#run the analysis to reproduce the output file. Here we just load the analyzed file
source('appendix\\appendix_B.R')
appendix_B_res <- run_appendixB(appendix_b_conf)
save_results_plot(appendix_B_res$summary)
```

```{r abstract-code, include=FALSE}
ucdb_conf <- init_analysis(Unconscious_Processing_analysis_lbl)
ucdb_dfs <- get_input_df(ucdb_conf)
res_summary_fn <- 'Unconscious Processing_Results.csv'
results_fld <- 'results'
alpha <- .05
results <- read.csv(paste(results_fld, res_summary_fn, sep=.Platform$file.sep))
ns_results <- results[results$directional_test.p > alpha,]
N_ns <- length(unique(ns_results$exp))
directional_effect_datasets <- setdiff(unique(results$exp), unique(ns_results$exp))
ns_N_participants <- ucdb_dfs %>%
  group_by(exp) %>%
  filter(!exp %in% directional_effect_datasets) %>% 
  summarise(n = length(unique(idv)))
# removing experiments where the same effect
N_unique_participants <- sum(ns_N_participants %>% 
         filter(!exp %in% c('Faivre et al._1_incong', 'Faivre et al._3_incong', 
                            'Faivre et al._4_incong', 'Hurme et al_2020_TMS_Red', 
                            'Stein & van Peelen_2020_3_PAS_2', 'Zerweck et al_2021_3_Duration_20',
                            'Zerweck et al_2021_3_Duration_30', 'Zerweck et al_2021_2_39', 
                            'Zerweck et al_2021_2_29')) %>%
                            dplyr::pull(n))
```

@@

# Simulating qualitative differences in unconscious effects

@@

First, we analyzed this simulated data using a two-sided paired t-test on the differences in mean RTs between the two conditions. This is the standard protocol for testing if unconscious processing took place. In both simulations, we obtained a null result, revealing no evidence for a difference in RT between the congruent and incongruent conditions (*qualitative differences*: `r apa_print(nde_t_test)$full_result`; *global null*: `r apa_print(sn_t_test)$full_result`). Importantly, in the *non-directional differences* simulation, all participants were affected by the experimental manipulation (that is, their true effect sizes were different from zero). Thus, this commonly used approach systematically misses true causal effects of the experimental manipulation whenever they are inconsistent between participants.

@@

# Reexamining unconscious effects within the Bayesian framework
```{r empiric-all-tests, include=FALSE}
n_empiric_ns <- uc_ns_results %>% filter(is_sim == FALSE) %>% pull(exp) %>% unique() %>% length()
n_empiric_ns_quid <- ns_quid_res %>% filter(is_sim == FALSE) %>% pull(exp) %>% unique() %>% length()
n_empiric_ns_oanova <- ns_OANOVA_res %>% filter(is_sim == FALSE) %>% pull(exp) %>% unique() %>% length()
p_pbt_MAP_zero <- ns_pbt_res %>% filter(is_sim == FALSE, pbt.MAP == 0)%>% pull(exp) %>% unique() %>% length() / n_empiric_ns
p_null_QUID <- ns_quid_res %>% filter(is_sim == FALSE, quid_bf < 1/bf_criteria)%>% pull(exp) %>% unique() %>% length() / n_empiric_ns_quid
res_per_exp <- uc_ns_results %>% group_by(exp) %>% summarise_all(mean)
skora_1_res <- res_per_exp %>% filter(exp == 'S1')
bm_3_res <- res_per_exp %>% filter(exp == 'BM3')
```

@@

# Testing within-participant sign-consistency across experimental psychology studies
```{r other-domains-tests, include=FALSE}
N_ns_no_UC <- sum(ns_sum_Ns %>% 
                    filter(type != "Unconscious Processing") %>% 
                    dplyr::pull(N))
N_ns_Confidence <- sum(ns_sum_Ns %>% 
                         filter(type %in% c('Confidence', 'Metacognitive Sensitivity')) %>%
                         dplyr::pull(N))
N_ns_Metacog <- ns_sum_Ns %>% filter(type == 'Metacognitive Sensitivity') %>% dplyr::pull(N)
N_ns_psycog <- null_results %>%
  filter(startsWith(type, 'Cognitive')) %>%
  mutate(sub_cat =  ifelse(startsWith(exp,'Adam'), 'VS', 
                           ifelse(startsWith(exp,'Battich'), 'Social' ,
                                  'Reproducibility'))) %>%
  group_by(sub_cat) %>% 
  summarise(n = n())
N_ns_Reproducibility <- N_ns_psycog %>% filter(sub_cat == 'Reproducibility') %>% pull(n)
N_ns_Attention <- N_ns_psycog %>% filter(sub_cat == 'VS') %>% pull(n)
N_ns_Social <- N_ns_psycog %>% filter(sub_cat == 'Social') %>% pull(n)

# extract individual experiments results
battich_res <- null_results %>% filter(startsWith(exp, 'Battich'))
ns_adam_res <- null_results %>% 
  filter(startsWith(exp,'Adam'), directional_test.p > alpha, signcon.p <= alpha)
# battich t-tests (directional)
battich_data <- read.csv("datasets\\cogdb\\Battich_etal_2021.csv")
## test for difference in effects between halves
compare_halves <- function(data, exp_label) {
  library(signcon)
  res_1st <- get_directional_effect(data %>% 
                                       filter(exp == exp_label, half == 1),
                                     idv = 'idv', iv = 'iv2', dv ='dv')
  scores_1st = res_1st$effect_per_id$score
  res_2nd <- get_directional_effect(data %>% 
                                       filter(exp == exp_label, half == 2),
                                     idv = 'idv', iv = 'iv2', dv ='dv')
  scores_2nd = res_2nd$effect_per_id$score
  return(t.test(scores_1st, scores_2nd,paired = TRUE))
}

res_battich_resp1_t <- compare_halves(battich_data[battich_data$exp == battich_res$exp[1],], battich_res$exp[1])
res_battich_resp2_t <- compare_halves(battich_data[battich_data$exp == battich_res$exp[2],], battich_res$exp[2])
res_battich_rt2_t <- compare_halves(battich_data[battich_data$exp == battich_res$exp[3],], battich_res$exp[3])
```

@@

\newpage
# Supplementary Table 1 {#STable-1}
``` {r supptable-1}
Study <- c('Biderman & Mudrik, 2018', 'Faivre et al., 2014', 'Stein & Peelen, 2021', 
'Zerweck et al., 2021', 'Benthien & Hesselmann, 2021', 'Hurme et al., 2020', 
'Skora et al., 2021', 'Chien et al., 2022')
Labels <- c('BM1-3', 'F1-8', 'SVP1-5','Z1-7','BH1','H1-4','S1-2','C1-3')
Topic <- c('Scene congruency', 'Multisensory integration', 'Location effects + PAS (detection)',
'Numerical Priming', 'Numerical Priming', 'Colors', 'Instrumental Learning', 'Semantic priming')
Paradigm <- c('Masking', 'Masking', 'CFS', 'Masking', 'CFS', 'TMS + Metacontrast Masking', 'Masking', 'CFS')
DV <- c('RT', 'RT', 'd\'', 'RT', 'RT', 'RT', 'd\'', 'RT')
Notes <- c('Replication study. For all experiments, log(RT) was used in the original analysis',
'Four experiments, two effects in each experiment (identical/different targets). For all experiments, log(RT) was used in the original analysis',
'Two experiments (3&4 in the paper), measuring effects in different prime-mask SOAs',
'Two experiments (2 and 3 in the original paper), measuring effects in different SOA / Contrast conditions',
'Interaction effect - prime congruency X location certainty',
'Redundant target effect (TMS / Masking X Blue / Red)',
'Regression to the mean as a confound according to authors',
'Word, Picture, and trait discrimination tasks')
studies_df <- data.frame(Study, Labels, Topic, DV, Notes)
apa_table(
  studies_df,
  caption = "Unconscious processing effects metadata",
  # align = c("l{2.5cm}", "l{1.5cm}", "l{2cm}", "l{0.8cm}", "l{7cm}"),
  font_size = 'footnotesize')
```

@@

# Supplementary Figure 2 - Sign-Consistency test results for datasets showing a directional effect
(ref:sfigure2caption) Supplementary Figure 2. The results of applying the Sign-Consistency test to significant directional effects (N = 7). The x-axis lists effect labels. Same conventions as Fig. 4.
```{r sfigure2, out.width="100%", fig.cap = "(ref:sfigure2caption)", warning = FALSE}
knitr::include_graphics("figures//plots//effect_plt_sign_con__res.png")
```

@@

``` {r appendix-A, warning = FALSE}
# run the analysis to reproduce the output file. Here we just load the analyzed file
# appendix_A_res <- read.csv('appendix\\results\\2023-05-02_11_32_45Appendix_A_QUID_OANOVA.csv')
appendix_A_analysis <- analyze_appendix_A(appendix_A_res)
quid_apndx_res <- appendix_A_analysis$quid_res
oanova_apndx_res <- appendix_A_analysis$oanova_res
```

@@

We used the simulation scheme described in the main text (see section ‘Simulating qualitative differences in unconscious effects’), to test the consequences of violating the equal within-individuals variance assumption for both QUID and the OANOVA test. We compared the distribution of Bayes factors and p-values obtained by applying QUID and the OANOVA test to generated data meeting and violating the equal within-participants variance assumption. In the first, equal-variance case, the within-individual standard deviation was low ($\sigma_{w}=`r sigma_w_equal`$) for all participants. In the second, unequal-variance case, the within-individual standard deviation was low ($\sigma_{w}=`r sigma_w_equal`$) for all participants except one, for whom it was set to a high value ($\sigma_{w}=`r sigma_w_unequal`$). As in the main simulation, effect sizes of each participant were sampled from a normal distribution centered at zero ($e_{i} \sim {\mathcal{N}}(0, \sigma_{b})$; where $e_{i}$ denotes the effect size of the ith participant). Within this framework, examined two scenarios: a qualitative differences scenario where participants are differentially affected by the experimental manipulation ($N_{p}=`r N_p_sensitivity`$, $\sigma_{b}=`r sigma_b_sensitivity`$), and a global null condition where all participants are unaffected by the experimental manipulation ($N_{p}=`r N_p_FAs`$, $\sigma_{b}=`r sigma_b_FAs`$). In both scenarios, we simulated random data in `r max_seed` iterations, and used the same number of trials per condition (the total number of trials, $N_{t}=`r 2*N_t`$).
To examine the tests’ specificity, we measured the proportion of iterations where evidence for an effect was erroneously found in the global null condition. In the equal-variance case, all iterations provided evidence for the lack of an effect according to QUID (all BFs < $\frac{1}{`r bf_criteria`}$). Similarly, nonsignificant results were found by the OANOVA test in `r oanova_apndx_res %>% filter(Analysis == sigma_b_FAs, Condition == sigma_w_equal,sig_OANOVA == FALSE) %>% pull(sig_prop)`% of the iterations (since the 95% CI of a random binomial parameter with p=.05 and n = `r max_seed` is [`r random_binom_CI_alpha[1]` `r random_binom_CI_alpha[2]`], the finding `r oanova_apndx_res %>% filter(Analysis == sigma_b_FAs, Condition == sigma_w_equal,sig_OANOVA == TRUE) %>% pull(sig_prop)`% false-positive results is expected due to randomness). However, in the unequal-variance case, false-positives were obtained in `r quid_apndx_res %>% filter(Analysis == sigma_b_FAs, Condition == sigma_w_unequal,sig_QUID == 'H1') %>% pull(sig_prop)`% of the QUID Bayes Factors (BF > `r bf_criteria`), and `r quid_apndx_res %>% filter(Analysis == sigma_b_FAs, Condition == sigma_w_unequal,sig_QUID == 'Inconclusive') %>% pull(sig_prop)`% showed inconclusive evidence. Again, the OANOVA test showed a similar pattern, detecting falsely significant effects in `r oanova_apndx_res %>% filter(Analysis == sigma_b_FAs, Condition == sigma_w_unequal,sig_OANOVA == TRUE) %>% pull(sig_prop)`% of the iterations. Thus, we show that the specificity of these tests is compromised by violations of the equal-variance assumption.
We then analyzed the tests’ outcomes in the qualitative differences scenario to examine their sensitivity. When the equal-variance assumption was met, both tests found evidence for an effect (all BFs > `r bf_criteria`, and all p-values < .05). In contrast, in the unequal-variance case, only `r quid_apndx_res %>% filter(Analysis == sigma_b_sensitivity, Condition == sigma_w_unequal,sig_QUID == 'H1') %>% pull(sig_prop)`% of QUIDs BFs showed evidence for an effect, whilst `r quid_apndx_res %>% filter(Analysis == sigma_b_sensitivity, Condition == sigma_w_unequal,sig_QUID == 'H0') %>% pull(sig_prop)`% showed evidence for no effect (the remaining `r quid_apndx_res %>% filter(Analysis == sigma_b_sensitivity, Condition == sigma_w_unequal,sig_QUID == 'Inconclusive') %>% pull(sig_prop)`% were inconclusive). Similarly, the OANOVA test found significant effects in only `r oanova_apndx_res %>% filter(Analysis == sigma_b_sensitivity, Condition == sigma_w_unequal,sig_OANOVA == TRUE) %>% pull(sig_prop)`% of the iterations. Hence, both tests missed true effects when the assumption was not met, demonstrating that their sensitivity is compromised by violations of the equal-variance assumption.

@@

# Appendix B. Comparing the power of the PBT and Sign-Consistency test {#Apndx-B}
To examine the differential sensitivity of PBT and the sign-consistency tests, we conducted a power analysis, simulating two scenarios under the simulations scheme described in the main text (see section ‘Simulating qualitative differences in unconscious effects’): First, a *qualitative differences* scenario where an effect exists for each participant but it is inconsistent within participants ($e_{i} \sim {\mathcal{N}}(0, \sigma_{b})$; where $\sigma_{b}$=2). Second, a *directional effect* scenario, with individual variation around a positive mean effect size  ($e_{i} \sim {\mathcal{N}}(1, \sigma_{b})$; where $\sigma_{b}$=2). For each scenario we manipulated the number of simulated participants ($N_{p}$=`r N_p[1]`/`r N_p[2]`/`r N_p[3]`) and trials ($N_{t}$=`r N_t[1]`/`r N_t[2]`/`r N_t[3]`) across `r max_seed` random iterations, with the within-participant SD ($\sigma_{w}$) set to 10 in both scenarios.
Statistical power was defined as the proportion of significant results in the Sign Consistency case, and as the proportion of $HDI_{95}$ intervals that do not include zero in the PBT case. While both tests were similarly sensitive when applied to well-powered datasets (e.g., when $N_{p}$=`r N_p[3]` or $N_{t}$=`r N_t[3]`), the sign-consistency test proved to be more sensitive in the remaining conditions (see Figure 7 in Ince et al., [-@ince2021a], for a comparison between the power of PBT and a standard t-test for the *directional effect* scenario).

>>>>

affiliation:
  - id            : "1"
    institution   : "Sagol School of Neuroscience, Tel Aviv University"
  - id            : "2"
    institution   : "University Grenoble Alpes, University Savoie Mont Blanc, CNRS, LPNC"
  - id            : "3"
    institution   : "School of Psychological Sciences, Tel Aviv University"
  - id            : "4"
    institution   : "Department of Psychological Sciences, Birkbeck, University of London"
  - id            : "5"
    institution   : "Wellcome Centre for Human Neuroimaging, UCL"

@@

library(groundhog)
groundhog.library(c(
  'ggplot2',
  'stringr',
  'gridExtra',
  'grid',
  'ggh4x',
  'ggtext',
  'ggridges',
  'ggpubr',
  'scales',
  'dplyr',
  'tidyr',
  'pracma',
  'patchwork',
  'HDInterval',
  'MCMCpack',
  'nleqslv'), '2023-04-10')
# separate github libraries
groundhog.library(c(
  'github::mufcitay/signcon'), '2023-04-10')

@@

```{r run-analyses, include=FALSE}
# run all analyses. The outputs are later used in the script
# to preprocess all datasets source the preprocessing script,
# sourcing this script will also download the up-to-date versiob of the confidence database from OSF (not the version used for analysis in this paper).
# source('datasets\\run_preprocessing.R')
# run all analysis on the preprocessed datasets
source('datasets_analysis\\run_all_analyses.R')

# sourcing the 'fig1sim' script generates the panels populating Figure 1 in the manuscript, and analyzes the simulated data with all available non-directional (here we used an edited version of this panels)
# tests, and t-tests.
source('figures\\fig1sim.R')
# sourcing the 'fig2_3' script generates figure 2, the lower panel of figure 3, and supplementary figure 1,2 (note that figure 3 was edited to also include the illustration in the upper panel of figure 3)
# it also analyzes the results of all unconscious processing datasets according to all tests
source('figures\\fig2_3.R')
# sourcing the 'fig4' script generates figure 4 (minor edits were applied to the resulting svg figure).
# it also analyzes the results of all datasets (including datasets from non-UC domains) according to the sign-consistency test.
source('figures\\fig4.R')

# the analysis and simulations for appendix A.
# to run the analysis again, uncomment the (commented) run_appendixA line and comment the read.csv line which reads the results of an existing simulations run.
source('appendix\\appendix_A.R')
appendixA_res <- run_appendixA(apndxA_conf_FAs, apndxA_conf_sensitivity)
# appendixA_res <- read.csv('appendix\\results\\2023-05-04_12_33_43Appendix_A_QUID_OANOVA.csv')

# the analysis and simulations for appendix B.
# to run the analysis again, uncomment the (commented) run_appendixB line and comment the read.csv line which reads the results of an existing simulations run (keeping the save_plot_appendixB line.
source('appendix\\appendix_B.R')
appendixB_res <- run_appendixB(apndx_b_conf)
# appendixB_res <- read.csv('appendix\\results\\2023-05-05_04_27_22Appendix_B.csv')
save_plot_appendixB(appendixB_res)
```

```{r abstract-code, include=FALSE}
# we used fixed numbers on the abstract, here is the code to recreate them.

# get the number of partcipants and effects in the ucdb
ucdb_conf <- init_analysis(Unconscious_Processing_analysis_lbl)
ucdb_dfs <- get_input_df(ucdb_conf)
res_summary_fn <- 'Unconscious Processing_Results.csv'
results_fld <- 'results'
alpha <- .05
# read the ucdb results file
results <- read.csv(paste(results_fld, res_summary_fn, sep=.Platform$file.sep))
# filter the number of ns (nonsignificant) directional effects
ns_results <- results[results$directional_test.p > alpha,]
N_ns <- length(unique(ns_results$exp))
directional_effect_datasets <- setdiff(unique(results$exp), unique(ns_results$exp))
# count participants
ns_N_participants <- ucdb_dfs %>%
  group_by(exp) %>%
  filter(!exp %in% directional_effect_datasets) %>% 
  summarise(n = length(unique(idv)))
# removing experiments where the same participants were included in different
# effects
N_unique_participants <- sum(ns_N_participants %>% 
         filter(!exp %in% c('Faivre et al._1_incong', 'Faivre et al._3_incong', 
                            'Faivre et al._4_incong', 'Hurme et al_2020_TMS_Red', 
                            'Stein & van Peelen_2020_3_PAS_2', 'Zerweck et al_2021_3_Duration_20',
                            'Zerweck et al_2021_3_Duration_30', 'Zerweck et al_2021_2_39', 
                            'Zerweck et al_2021_2_29')) %>%
                            dplyr::pull(n))
```

@@

# Simulating non-directional unconscious effects

@@

First, we analyzed this simulated data using a two-sided paired t-test on the differences in mean RTs between the two conditions. This is the standard protocol for testing if unconscious processing took place. In both simulations, we obtained a null result, revealing no evidence for a difference in RT between the congruent and incongruent conditions (*non-directional differences*: `r apa_print(nde_t_test)$full_result`; *global null*: `r apa_print(sn_t_test)$full_result`). Importantly, in the *non-directional differences* simulation, all participants were affected by the experimental manipulation (that is, their true effect sizes were different from zero). Thus, this commonly used approach systematically misses true causal effects of the experimental manipulation whenever they are inconsistent between participants.

@@

# Reexamining unconscious effects within the Bayesian framework
```{r empiric-all-tests, include=FALSE}
# get the counts of experiments for the section (uc datasets), reading from the enviroment created by soucing the fig2_3.R script
n_empiric_ns <- uc_ns_results %>% filter(is_sim == FALSE) %>% pull(exp) %>% unique() %>% length()
n_empiric_ns_quid <- ns_quid_res %>% filter(is_sim == FALSE) %>% pull(exp) %>% unique() %>% length()
n_empiric_ns_oanova <- ns_OANOVA_res %>% filter(is_sim == FALSE) %>% pull(exp) %>% unique() %>% length()
p_pbt_MAP_zero <- ns_pbt_res %>% filter(is_sim == FALSE, pbt.MAP == 0)%>% pull(exp) %>% unique() %>% length() / n_empiric_ns
p_null_QUID <- ns_quid_res %>% filter(is_sim == FALSE, quid_bf < 1/bf_criteria)%>% pull(exp) %>% unique() %>% length() / n_empiric_ns_quid
# get the results of individual experiments with significant sign-consistency.
# in the results data frame there are multiple lines per exp (listing the null distribution per experiment). We average across rows to get the repeating statistics per experiment.
res_per_exp <- uc_ns_results %>% group_by(exp) %>% summarise_all(mean)
skora_1_res <- res_per_exp %>% filter(exp == 'S1')
bm_3_res <- res_per_exp %>% filter(exp == 'BM3')
```

@@

# Testing within-participant sign-consistency across experimental psychology studies
```{r other-domains-tests, include=FALSE}
# get the counts of experiments for the section (from all domains), reading from the enviroment created by soucing the fig4.R script
N_ns_no_UC <- sum(ns_sum_Ns %>% 
                    filter(type != "Unconscious Processing") %>% 
                    dplyr::pull(N))
N_ns_Confidence <- sum(ns_sum_Ns %>% 
                         filter(type %in% c('Confidence', 'Metacognitive Sensitivity')) %>%
                         dplyr::pull(N))
N_ns_Metacog <- ns_sum_Ns %>% filter(type == 'Metacognitive Sensitivity') %>% dplyr::pull(N)
N_ns_psycog <- null_results %>%
  filter(startsWith(type, 'Cognitive')) %>%
  mutate(sub_cat =  ifelse(startsWith(exp,'Adam'), 'VS', 
                           ifelse(startsWith(exp,'Battich'), 'Social' ,
                                  'Reproducibility'))) %>%
  group_by(sub_cat) %>% 
  summarise(n = n())
N_ns_Reproducibility <- N_ns_psycog %>% filter(sub_cat == 'Reproducibility') %>% pull(n)
N_ns_Attention <- N_ns_psycog %>% filter(sub_cat == 'VS') %>% pull(n)
N_ns_Social <- N_ns_psycog %>% filter(sub_cat == 'Social') %>% pull(n)

# extract individual experiments results
battich_res <- null_results %>% filter(startsWith(exp, 'Battich'))
ns_adam_res <- null_results %>% 
  filter(startsWith(exp,'Adam'), directional_test.p > alpha, signcon.p <= alpha)

# for the multisensory experiment (Battich et al.), we also examine whether the results can be explained by a directional order effect
# read the whole dataset
battich_data <- read.csv("datasets\\cogdb\\Battich_etal_2021.csv")
# test for difference in effects between halves (we included only the individual and joint attention condition, so halves = blocks)
compare_halves <- function(data, exp_label) {
  # get the directional effect for each of the halves
  res_1st <- get_directional_effect(data %>% 
                                       filter(exp == exp_label, half == 1),
                                     idv = 'idv', iv = 'iv2', dv ='dv')
  scores_1st = res_1st$effect_per_id$score
  res_2nd <- get_directional_effect(data %>% 
                                       filter(exp == exp_label, half == 2),
                                     idv = 'idv', iv = 'iv2', dv ='dv')
  scores_2nd = res_2nd$effect_per_id$score
  # use a t-test to compare effect scores between halves (is there a condition-order effect?)
  return(t.test(scores_1st, scores_2nd,paired = TRUE))
}
# test for a directional condition-order effect in all of the cases where a non-directional effect was found (three cases our of four) 
res_battich_resp1_t <- compare_halves(battich_data[battich_data$exp == battich_res$exp[1],], battich_res$exp[1])
res_battich_resp2_t <- compare_halves(battich_data[battich_data$exp == battich_res$exp[2],], battich_res$exp[2])
res_battich_rt2_t <- compare_halves(battich_data[battich_data$exp == battich_res$exp[3],], battich_res$exp[3])
```

@@

\newpage
# Supplementary Table 1 {#STable-1}
``` {r supptable-1}
# create the supplementary table by code
Study <- c('Biderman & Mudrik, 2018', 'Faivre et al., 2014', 'Stein & Peelen, 2021', 
'Zerweck et al., 2021', 'Benthien & Hesselmann, 2021', 'Hurme et al., 2020', 
'Skora et al., 2021', 'Chien et al., 2022')
Labels <- c('BM1-3', 'F1-8', 'SVP1-5','Z1-7','BH1','H1-4','S1-2','C1-3')
Topic <- c('Scene congruency', 'Multisensory integration', 'Location effects + PAS (detection)',
'Numerical Priming', 'Numerical Priming', 'Colors', 'Instrumental Learning', 'Semantic priming')
Paradigm <- c('Masking', 'Masking', 'CFS', 'Masking', 'CFS', 'TMS + Metacontrast Masking', 'Masking', 'CFS')
DV <- c('RT', 'RT', 'd\'', 'RT', 'RT', 'RT', 'd\'', 'RT')
Notes <- c('Replication study. For all experiments, log(RT) was used in the original analysis',
'Four experiments, two effects in each experiment (identical/different targets). For all experiments, log(RT) was used in the original analysis',
'Two experiments (3&4 in the paper), measuring effects in different prime-mask SOAs',
'Two experiments (2 and 3 in the original paper), measuring effects in different SOA / Contrast conditions',
'Interaction effect - prime congruency X location certainty',
'Redundant target effect (TMS / Masking X Blue / Red)',
'Regression to the mean as a confound according to authors',
'Word, Picture, and trait discrimination tasks')
studies_df <- data.frame(Study, Labels, Topic, DV, Notes)
# print the table according to apa style using a small font size
apa_table(
  studies_df,
  caption = "Unconscious processing effects metadata",
  font_size = 'footnotesize')
```

@@

# Supplementary Figure 2 - Sign-Consistency test results for datasets showing a directional effect
(ref:sfigure2caption) Supplementary Figure 2. The results of applying the Sign-Consistency test to significant directional effects (N = 7). The x-axis lists effect labels. Same conventions as Fig. 3.
```{r sfigure2, out.width="100%", fig.cap = "(ref:sfigure2caption)", warning = FALSE}
knitr::include_graphics("figures//plots//effect_plt_sign_con__res.png")
```

@@

``` {r appendix-A, warning = FALSE}
# use the results of running the appendixA script above, analyze the results for QUID and OANOVA separetly
appendix_A_analysis <- analyze_appendix_A(appendixA_res)
quid_apndx_res <- appendix_A_analysis$quid_res
oanova_apndx_res <- appendix_A_analysis$oanova_res
# extract simulation paramters for each scenario (FAs and Sensitivity analysis)
apndxA_sigma_w_low <- min(apndxA_conf_FAs$params$sigma_w)
apndxA_sigma_w_unequal <- max(apndxA_conf_FAs$params$sigma_w)
apndxA_FA_sigma_b <- dplyr::first(apndxA_conf_FAs$params$sigma_b)
apndxA_sensitivity_sigma_b <- dplyr::first(apndxA_conf_sensitivity$params$sigma_b)
apndxA_FA_Np <- dplyr::first(apndxA_conf_FAs$params$N_p)
apndxA_sensitivity_Np <- dplyr::first(apndxA_conf_sensitivity$params$N_p) 
apndxA_mu <- dplyr::first(apndxA_conf_FAs$params$mu)
# we multiply by 2 because the simulation expects number of trials per condition and we report the total amount of trials
apndxA_Nt <- 2 * dplyr::first(apndxA_conf_FAs$params$N_t)
apndxA_iterations <- max(apndxA_conf_FAs$results$seeds)
```

@@

We used the simulation scheme described in the main text (see section ‘Simulating non-directional unconscious effects’), to test the consequences of violating the equal within-individuals variance assumption for both QUID and the OANOVA test. We compared the distribution of Bayes factors and p-values obtained by applying QUID and the OANOVA test to generated data meeting and violating the equal within-participants variance assumption. In the first, equal-variance case, the within-individual standard deviation was low ($\sigma_{w}=`r apndxA_sigma_w_low`$) for all participants. In the second, unequal-variance case, the within-individual standard deviation was low ($\sigma_{w}=`r apndxA_sigma_w_low`$) for all participants except one, for whom it was set to a high value ($\sigma_{w}=`r apndxA_sigma_w_unequal`$). As in the main simulation, effect sizes of each participant were sampled from a normal distribution centered at zero ($e_{i} \sim {\mathcal{N}}(`r apndxA_mu`, \sigma_{b})$; where $e_{i}$ denotes the effect size of the ith participant). Within this framework, examined two scenarios: a non-directional differences scenario where participants are differentially affected by the experimental manipulation ($N_{p}=`r apndxA_sensitivity_Np`$, $\sigma_{b}=`r apndxA_sensitivity_sigma_b`$), and a global null condition where all participants are unaffected by the experimental manipulation ($N_{p}=`r apndxA_FA_Np`$, $\sigma_{b}=`r apndxA_FA_sigma_b`$). In both scenarios, we simulated random data in `r apndxA_iterations` iterations, and used the same number of trials per condition (the total number of trials, $N_{t}= `r apndxA_Nt`$).
To examine the tests’ specificity, we measured the proportion of iterations where evidence for an effect was erroneously found in the global null condition. In the equal-variance case, all iterations provided evidence for the lack of an effect according to QUID (all BFs < $\frac{1}{`r bf_criteria`}$). Similarly, nonsignificant results were found by the OANOVA test in `r oanova_apndx_res %>% filter(Analysis == sigma_b_FAs, Condition == sigma_w_equal,sig_OANOVA == FALSE) %>% pull(sig_prop)`% of the iterations (since the 95% CI of a random binomial variable with $p= `r apndxA_alpha`$ and n = `r apndxA_iterations` is [`r random_binom_CI_alpha[1]` `r random_binom_CI_alpha[2]`], the finding `r oanova_apndx_res %>% filter(Analysis == sigma_b_FAs, Condition == sigma_w_equal,sig_OANOVA == TRUE) %>% pull(sig_prop)`% false-positive results is expected due to randomness). However, in the unequal-variance case, false-positives were obtained in `r quid_apndx_res %>% filter(Analysis == sigma_b_FAs, Condition == sigma_w_unequal,sig_QUID == 'H1') %>% pull(sig_prop)`% of the QUID Bayes Factors (BF > `r bf_criteria`), and `r quid_apndx_res %>% filter(Analysis == sigma_b_FAs, Condition == sigma_w_unequal,sig_QUID == 'Inconclusive') %>% pull(sig_prop)`% showed inconclusive evidence. Again, the OANOVA test showed a similar pattern, detecting falsely significant effects in `r oanova_apndx_res %>% filter(Analysis == sigma_b_FAs, Condition == sigma_w_unequal,sig_OANOVA == TRUE) %>% pull(sig_prop)`% of the iterations. Thus, we show that the specificity of these tests is compromised by violations of the equal-variance assumption.
We then analyzed the tests’ outcomes in the non-directional differences scenario to examine their sensitivity. When the equal-variance assumption was met, both tests found evidence for an effect (all BFs > `r bf_criteria`, and all p-values < `r apndxA_alpha`). In contrast, in the unequal-variance case, only `r quid_apndx_res %>% filter(Analysis == sigma_b_sensitivity, Condition == sigma_w_unequal,sig_QUID == 'H1') %>% pull(sig_prop)`% of QUIDs BFs showed evidence for an effect, whilst `r quid_apndx_res %>% filter(Analysis == sigma_b_sensitivity, Condition == sigma_w_unequal,sig_QUID == 'H0') %>% pull(sig_prop)`% showed evidence for no effect (the remaining `r quid_apndx_res %>% filter(Analysis == sigma_b_sensitivity, Condition == sigma_w_unequal,sig_QUID == 'Inconclusive') %>% pull(sig_prop)`% were inconclusive). Similarly, the OANOVA test found significant effects in only `r oanova_apndx_res %>% filter(Analysis == sigma_b_sensitivity, Condition == sigma_w_unequal,sig_OANOVA == TRUE) %>% pull(sig_prop)`% of the iterations. Hence, both tests missed true effects when the assumption was not met, demonstrating that their sensitivity is compromised by violations of the equal-variance assumption.

@@

```{r appendix_b}
# use the results of running the appendixB script above, to extract the simulation parameters
apndxB_sig_b <- dplyr::first(apndx_b_conf$params$sigma_b)
apndxB_sig_w <- dplyr::first(apndx_b_conf$params$sigma_w)
# we multiply by 2 because the simulation expects number of trials per condition and we report the total amount of trials
apndxB_Nt <- 2 * unique(apndx_b_conf$params$N_t)
apndxB_Np <- unique(apndx_b_conf$params$N_p)
apndxB_de_mu <- max(apndx_b_conf$params$mu)
apndxB_nd_mu <- min(apndx_b_conf$params$mu)
apndxB_iterations <- max(apndx_b_conf$results$seeds)
```
